
# Program Roll-Out {#procedure}

This page primarily serves as a procedural overview, so future Eagle I.O cohorts can implement and manage the Mentorship program.

Procedurally, Eagle I.O'ers:

1) Guage interest and availability via administering a  [survey](https://survey.az1.qualtrics.com/jfe/form/SV_1TFZ0AIYBpsyh6Z) sent by the program director in July
    +  Several follow-up attempts are made during the summer 
    + Template documents:^[Note these documents are only available to individuals who have an e-mail address with the "montclair.edu" domain]  
        * [To Second Year Mentors](https://drive.google.com/open?id=1oDPE6IKPpk-vFezMzAU6uGP9HiTDfH4DSmJT1TQdXYU)  
        * [To First Year Mentees](https://drive.google.com/open?id=1BWLyBbBIcMEBeRxTNhBaLzbWkEPXThcO44qSh4HwTpw)  
        * [First Two Events](https://docs.google.com/document/d/1o_W0KReXqGGoR6jn1zabX6syhJ2sNjMZH8RPBwtfbnI/edit?usp=sharing)

2) Eagle IO consultants match interested mentors and mentees
    + This is done prior to the annual [baseball game](http://njjackals.pointstreaksites.com/view/njjackals/home-page-657/) event
3) Matches are introduced at (or before) the baseball game and discuss future events (see Chapter \@ref(timeline)) 
4) The program is monitored periodically (see Chapter \@ref(Eagle) "Eagle I.O Responsibilities")

## Responsibility Calendar (Fall 2019) {#fall19}

```{r Fall2019, echo=FALSE, warning=FALSE}

## https://www.rdocumentation.org/packages/TeachingDemos/versions/2.10/topics/cal

library(TeachingDemos)
# cal(2019)                                           ## Yearly calendars
# cal(2020)

## Colors in 8 digit hex: https://www.quackit.com/css/color/values/css_hex_color_notation_8_digits.cfm

setday <- cal(8,2019)                               ## August events
setday(29)
text(0.5,0.5, "Jackal's\nGame")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <- cal(9,2019)                               ## September
setday(2)
text(0.5,0.5, "SAM")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(9)
text(0.5,0.5, "KRISTINA")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(16)
text(0.5,0.5, "TAYLOR")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(23)
text(0.5,0.5, "RENATA")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(30)
text(0.5,0.5, "DANIELLE")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(4)
text(0.5,0.5, "First Day\nof Class")

setday(6)
text(0.5,0.5, "Orientation")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(27)
text(0.5,0.5, "Mentor and\nMentee\nMeet Up")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <- cal(10,2019)                               ## October

setday(7)
text(0.5,0.5, "NISHI")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(14)
text(0.5,0.5, "DEHLIA")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(28)
text(0.5,0.5, "DANIELLE")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(21)
text(0.5,0.5, "ELESE\n& LinkedIN")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday(10)
text(0.5,0.5, "Metro")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday <- cal(11,2019)                               ## November

setday(4)
text(0.5,0.5, "ELESE")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(11)
text(0.5,0.5, "DEHLIA")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(18)
text(0.5,0.5, "RENATA")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(25)
text(0.5,0.5, "TAYOR\n& Plentiful\nPotluck")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday(14)
text(0.5,0.5, "Metro")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(8)
text(0.5,0.5, "Double\nDining\nDate")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(28)
text(0.5,0.5, "Thanksgiving\nDay")


setday <- cal(12,2019)                               ## December

setday(2)
text(0.5,0.5, "KRISTINA")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(16)
text(0.5,0.5, "NISHI")
rect(-0.04,-0.04,1.04,1.04, col="#4600B433")

setday(9)
text(0.5,0.5, "SAM\n& Gear up\nfor Finals")
rect(-0.04,-0.04,1.04,1.04, col="#ff000066")

setday(18)
text(0.5,0.5, "Senior\nSoiree")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(13)
text(0.5,0.5, "Metro")
rect(-0.04,-0.04,1.04,1.04, col="#32CD3244")

setday(12)
text(0.5,0.5, "Last Day\nof Classes")

setday(19)
text(0.5,0.5, "End of\nthe Semester")

```

## Responsibility Calendar (Spring 2019) {#spring20}

```{r Spring2020, echo=FALSE, warning=FALSE}

cal(1,2020)
cal(2,2020)
cal(3,2020)
cal(4,2020)
cal(5,2020)

```